Digging Deeper Into the State of the Practice for Domain Specific Research Software

### 2022-02-18 StateOfPractice/Papers/ICCS-2022-SOP_MethodologyPlusExamples/DigDeep.tex
Revisions to Section 4: Comparison of Artifacts to Other Research Software
Revisions to Section 5: Comparison of Tools to Other Research Software

The results for the LBM example are shown below.  The majority of LBM generated
artifacts correspond to general recommendations from research software
developers.  For LBM, a union of the three categories mostly corresponds to
general research software recommendations (Table~\ref{Tbl_Guidelines}). Areas
where LBM developers could improve include providing: API documentation, a
roadmap, a code of conduct, programming style guide, and uninstall instructions.

@@

% \begin{table}[h!]
% \begin{center}
% \begin{tabular}{ p{12 cm}}
% %\toprule
% \textbf{Common}\\
% \midrule
% Developer List, Issue Tracker, Dependency List, Installation Guide, Theory
% Notes, Related Publications, Build Files, README File, License, Tutorial,
% Version Control\\
% %\midrule
% \textbf{Less Common}\\
% \midrule
% Change Log, Design Doc., Functional Spec., Performance Info., Test Cases, User
% Manual\\
% %\midrule
% \textbf{Rare}\\
% \midrule
% API Doc., Developer Manual, FAQ, Verification Plan, Video Guide, Requirements
% Spec.\\
% %\bottomrule
% \end{tabular}
% \caption{Artifacts Present in LBM Packages, Classified by Frequency}
% \label{artifactspresent}
% \end{center}
% \end{table}

@@

To answer \rqref{RQ_CompareToolsProjMngmnt} we need to summarize tools that are
visible in the repositories and that are mentioned during the developer
interviews. Software tools are used to support the development, verification,
maintenance, and evolution of software, software processes, and
artifacts~\cite[p.\ 501]{GhezziEtAl2003}. Development tools support the
development of end products, but do not become part of them, unlike dependencies
that remain in the application once it is released \cite[p.\
506]{GhezziEtAl2003}. As an example, the tools found for LBM software packages
are as follows:

@@

Once the data on tools is collected, the use of two specific tools should be
compared to research software norms: version control and continuous integration.
A little over 10 years ago version control was estimated to be used in only 50\%
of research software projects \cite{Nguyen-HoanEtAl2010}, but even at that time
\cite{Nguyen-HoanEtAl2010} noted an increase from previous usage levels. More
recently, version control usage rates for active mesh generation, geographic
information system and statistical software packages were close to
100~\cite{Smith2018}.  Almost every software guide cited in
Section~\ref{Sec_CompareArtifacts} includes the advice to use version control.
For LBM packages 67\% of LBM packages use version control (GitHub, GitLab or
CVS). The high usage of version control tools in LBM software matches the trend
in research software in general.

>>>>

The majority of LBM generated artifacts (summarized below) correspond to general
recommendations from research software developers.  For LBM, a union of the
three categories mostly corresponds to general research software recommendations
(Table~\ref{Tbl_Guidelines}). Areas where LBM developers could improve include
providing: API documentation, a roadmap, a code of conduct, programming style
guide, and uninstall instructions.

@@

@@

Software tools are used to support the development, verification, maintenance,
and evolution of software, software processes, and artifacts~\cite[p.\
501]{GhezziEtAl2003}. Development tools support the development of end products,
but do not become part of them, unlike dependencies that remain in the
application once it is released \cite[p.\ 506]{GhezziEtAl2003}. To answer
\rqref{RQ_CompareToolsProjMngmnt} we summarize tools that are visible in the
repositories and that are mentioned during the developer interviews.  As an
example, the tools found for LBM software packages are as follows:

@@

Once the data on tools is collected, the use of two specific tools should be
compared to research software norms: version control and continuous integration.
A little over 10 years ago version control was estimated to be used in only 50\%
of research software projects \cite{Nguyen-HoanEtAl2010}, but even at that time
\cite{Nguyen-HoanEtAl2010} noted an increase from previous usage levels. More
recently, version control usage rates for active mesh generation, geographic
information system and statistical software packages were close to
100\%~\cite{Smith2018}.  Almost every software guide cited in
Table~\ref{Tbl_Guidelines} includes the advice to use version control. For LBM
packages 67\% use version control (GitHub, GitLab or CVS). The high usage of
version control tools in LBM software matches the trend in research software in
general.
